IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/intro.tex
Pass in intro, shrinking a bit

Inspired by OS research~\cite{}, we present a \textit{coarse-grained} dynamic
IFC monitor to JavaScript (as specified by ECMAScript~\cite{}). Specifically,
JavaScript code is divided into relatively coarse computational units
(i.e. workers), each with a single label dictating its security policy. As a
result, it is just enough to track communication between isolated computational
units.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This technique provides a number of advantages: (1) no changes to JavaScript's
semantics when adding IFC ---our approach only exposes an small API to
JavaScript code in order to interact with the monitor---, and
% which (2) allows
%the reuse of existing programs.  Furthermore,
(2) reduced runtime overhead because checks only need to be performed at isolation
boundaries instead of at every instruction in the code~\cite{JSFlow}.
%, compared to fine-grained systems were the runtime overhead can be
% impractical~\cite{JSFlow}.
Finally, (3) associating a single security label with the entire computational
unit simplifies understanding and reasoning about the correctness of the system,
without reasoning about most of the semantics details of JavaScript.
% underlying programming language, i.e., JavaScript.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained dynamic information
    flow control monitor which is agnostic to non-IFC constructs.
    %We show how a
  \item We show non-interefence results when target languages exhibit a notion
    of isolated computations and control of external side-effects.
    %large class of target languages can be combined with this IFC language and
    %prove that the result provides
    %non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  %% \item We provide a proof technique to show the non-interference
  %% of a concrete semantics for a potentially optimized IFC language
  %% by means of an isomorphism and show a class of restrictions on
  %% the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item
  %We have implemented an IFC system based on these semantics
  %or Node.js, and
  We connect our formalism to COWL~\cite{swapi}, a
  client-side IFC monitor for JavaScript in Firefox.
  %Furthermore, we outline an implementation for the C programming
  %language.
  %(Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, labeled references, or a
  notion of clearance. %(Section~\ref{sec:extensions})
\end{itemize}

>>>>

Inspired by OS research~\cite{Zeldovich:2006}, we present a
\textit{coarse-grained} dynamic IFC monitor to JavaScript (as specified by
ECMAScript~\cite{ecma}). Specifically, JavaScript code is divided into relatively
coarse computational units (i.e. workers), each with a single label dictating
its security policy. As a result, it is just enough to track communication
between isolated computational units.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This technique provides a number of advantages: (1) no changes to JavaScript's
semantics when adding IFC ---our approach only exposes an small API to
JavaScript code in order to interact with the monitor---, and
% which (2) allows
%the reuse of existing programs.  Furthermore,
(2) reduced runtime overhead because checks only need to be performed at isolation
boundaries instead of at every instruction in the code~\cite{JSFlow}.
%, compared to fine-grained systems were the runtime overhead can be
% impractical~\cite{JSFlow}.
Finally, (3) associating a single security label with the entire computational
unit simplifies understanding and reasoning about the correctness of the system,
without reasoning about most of the semantics details of JavaScript.
% underlying programming language, i.e., JavaScript.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a generic coarse-grained dynamic
    information flow control monitor which is agnostic to non-IFC constructs.
    %We show how a
  \item We show non-interefence results when target languages exhibit a notion
    of isolated computations and control of external side-effects.
    %large class of target languages can be combined with this IFC language and
    %prove that the result provides
    %non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  %% \item We provide a proof technique to show the non-interference
  %% of a concrete semantics for a potentially optimized IFC language
  %% by means of an isomorphism and show a class of restrictions on
  %% the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item
  %We have implemented an IFC system based on these semantics
  %or Node.js, and
  We connect our formalism to COWL~\cite{swapi}, a
  client-side IFC monitor for JavaScript in Firefox.
  %Furthermore, we outline an implementation for the C programming
  %language.
  %(Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, labeled references, or a
  notion of clearance. %(Section~\ref{sec:extensions})
\end{itemize}
